Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-19 docs/thesis/chap-evaluation.tex
added sample equations, indexing tests and quality of results

Eq5 & \scriptsize{Electron effective mass in solid state physics} & \scriptsize {\codefont <math > <msup> <msup> <mi>m</mi> <mo>*</mo> </msup> <mn>-1</mn> </msup> <mo>==</mo> <mfrac> <mn>1</mn> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> </mfrac> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <mi>E</mi> </math>
 } & \scriptsize{${m^*}^{-1} = \frac{1}{\hbar^{2}} \nabla_k \nabla_k E$ } \\ \hline

>>>>

Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math> <msub> <mi>G</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <msub> <mi>R</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mi>R</mi> <msub> <mi>g</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <mfrac> <mrow> <mn>8</mn> <mi>π</mi> <mi>G</mi> </mrow> <msup> <mi>c</mi> <mn>4</mn> </msup> </mfrac> <msub> <mi>T</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> </math>
 </math>
 } & \scriptsize{$G_{\mu\nu}\equiv R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline
